Exploratory Figures

### 2024-06-18 Manuscript Analysis/exploratory_figures.Rmd
intelligibility plots

@@

@@

>>>>

## Peak Pupil Dilation

### LME Model

peak_pupil <- pupil_df |>  
  dplyr::filter(time_norm >= 500) |>
  dplyr::group_by(subject, trial) |>
  # filtering out timebins 1000 ms after phrase offset
  dplyr::filter(time_norm<= max(time_norm) - 2000) |>
  dplyr::ungroup() |>
  # Getting Peak Pupil Dilation Value
  dplyr::group_by(subject, trial, speaker, code, intel) |>
  dplyr::summarize(peak_pupil = max(normed_pupil)) |>
  dplyr::ungroup() |>
  dplyr::mutate(trial_c = trial - 6)

peak_pupil_model <- glmmTMB(peak_pupil ~ intel*speaker + (1|subject), data = peak_pupil)
#summary(peak_pupil_model)

peak_pupil_model_2 <- glmmTMB(peak_pupil ~ poly(intel, degree = 2)*speaker + (1|subject), data = peak_pupil)
#summary(peak_pupil_model_2)

anova(peak_pupil_model, peak_pupil_model_2)

sjPlot::tab_model(peak_pupil_model, peak_pupil_model_2,
                  file = "Tables/peak_pupil_intel_model.html")

### Plot

peak_pupil |>
  dplyr::mutate(speaker = factor(speaker, levels = c("Control", "ALS"),
                                   labels = c("Neurotypical", "ALS")),
                color = ifelse(speaker == "ALS", my_pal[5], my_pal[1])) |>
  ggplot() +
  aes(x = intel,
      y = peak_pupil,
      color = speaker) +
  geom_line(method = "lm", stat = "smooth", aes(group = subject), alpha = .3) +
  geom_line(stat = "smooth", method = "lm", size = 2) +
  labs(x = "Intelligibility (% Words Correct)", 
       y = "Peak Pupil Dilation (Arbitrary Units",
       color = "Speaker", fill = "Speaker", linetype = "Speaker", shape = "Speaker") +
  facet_wrap("speaker") +
  theme_bw() +
  theme(legend.position = "bottom",
        aspect.ratio = 1) +
  coord_cartesian(ylim = c(0, 850)) +
  scale_color_manual(values = c(my_pal[1], my_pal[5]))

ggsave("Figures/pupil_intel.png", plot = last_plot())

@@

### LME Model

@@

ple_data <- rio::import("Cleaned Data/cleaned_ple_data.csv") |>
  dplyr::left_join(phrase_acc, by = c("subject", "trial")) |>
  dplyr::mutate(speaker = factor(speaker, levels = c("Control", "ALS")),
                trial_c = trial - 6,
                rep_acc = factor(rep_acc, levels = c("accurate", "inaccurate"))) |>
  dplyr::filter(!is.na(rep_acc)) |>
  dplyr::filter(effort_rating > 0)

ple_model <- glmmTMB(effort_rating ~ intel*speaker +
                       (trial_c|subject) + (trial_c|code), data = ple_data)
summary(ple_model)

### Plot

ple_data |>
  dplyr::mutate(speaker = factor(speaker, levels = c("Control", "ALS"),
                                   labels = c("Neurotypical", "ALS")),
                color = ifelse(speaker == "ALS", my_pal[5], my_pal[1])) |>
  ggplot() +
  aes(x = intel,
      y = effort_rating,
      color = speaker) +
  geom_line(method = "lm", stat = "smooth", aes(group = subject), alpha = .3) +
  geom_line(stat = "smooth", method = "lm", size = 2) +
  labs(x = "Intelligibility (% Words Correct)", 
       y = "Peak Pupil Dilation (Arbitrary Units",
       color = "Speaker", fill = "Speaker", linetype = "Speaker", shape = "Speaker") +
  facet_wrap("speaker") +
  theme_bw() +
  theme(legend.position = "bottom",
        aspect.ratio = 1) +
  coord_cartesian(ylim = c(0, 7)) +
  scale_color_manual(values = c(my_pal[1], my_pal[5]))

ggsave("Figures/ple_intel.png", plot = last_plot())
